### 2018-04-29 paper/intro.tex

Constructing a system that provides anonymous communication is a very
challenging issue. The last decades, we have witnessed a
 huge set of attempts at building privacy preserving and anonymous p2p
 networks \cite{Clarke:2001, Gnunet2002, Freedman:2002, Nambiar:2006,
   Rennhard:2002}. They are mainly based on onion
 routing concepts \cite{Chaum:1981}, with some improvements to perform node
 discovery in a distributed manner, which are otherwise
centralized in traditional onion routing schemes. However, due to high
churn of peer-to-peer networks, performance of these systems is
discouraging \cite{LeBlond:2013}; churn implies frequent
reconstruction of routes, which is very expensive.

>>>>

Constructing a system that provides anonymous communication is a very
challenging issue. The last decades, we have witnessed a
 huge set of attempts at building privacy preserving and anonymous p2p
 networks \cite{Clarke:2001, Gnunet2002, Freedman:2002, Nambiar:2006,
   Rennhard:2002}. They are mainly based on onion
 routing concepts \cite{Chaum:1981}, with some improvements to perform node
 discovery in a distributed manner, which are otherwise
centralized in traditional onion routing schemes. However, due to high
churn of peer-to-peer networks, performance of these systems is
discouraging \cite{LeBlond:2013}; churn implies frequent
reconstruction of routes, which is very expensive. In comparison, Tor
\cite{Dingledine:2004}, one of the most popular anonymous network
mitigate lack of performances of anonymity at the cost of a
centralized design through the use of directory
servers to advertise available trusted nodes to bootstrap Onion
routes.

In this paper, we introduce SPORES, Stateless Predictive Onion Routing
for E-Squads, a novel approach to perform a decentralized, autonomous, and self-organizing 
file sharing among users' devices while preserving the users’ privacy
in terms of data and metadata. The key originality of our approach is
to consider that users share files in ...

Our contributions are as follows:

% Cashmere: resilient anonymous routing.
% Route fingerprinting in anonymous communications.
% Bridging and fingerprinting:
% Epistemic attacks on route selection
% Breaking the collusion detection mechanism of morphmix
% Denial of service or denial of security? How attacks
% on reliability can compromise anonymity
